\chapter{Abstract}

\subsubsection*{English}

This report describes the 4th semester project at Aarhus University School of Engineering, with Information technology as the field of study. The thesis issue addresses the design and implementation of a cash register which is easy to use even when the bartender have had a few. The thesis presentation was giving from Katrines Kælder and that is why this project is designed with the purpose of a cash register to Katrines Kælder which is user-friendly for bartenders to use.
\newline
\newline
The thesis issue is realized by a bartender using the cash register through a \gls{GUI} which is designed in \gls{WPF}. Through the \gls{GUI} communication is made to the database using the business logic. A Bartender can using the \gls{GUI} perform sale and return of products. A Web Api \fxnote{gls} is designet which the administartor kan use to edit data in the database.
\newline
\newline
The entire project will contain a cash register with a \gls{GUI} which can print a receipt and complete a cash payment, with the option of developing more payment options. Furthermore a Web Api \fxnote{gls} is also developed which can add, edit and remove products, product groups, product types and product tabs in the database.
\newline
\newline
The development process is conducted using a Scrum timetable, which is iteratively. Which is in case has consisted of 2 week long sprints. In these iterations the documentation and rapport has been developed. The documentation is structured after the N+1 \fxnote{gls} model. As the development process was coming to the end the documentation has been worked on and changed according to the growing knowledge working on this project has provided. From the thorough work on this project a system, project and documentation has been achieved.